### 2015-08-04 implementation-virtual-deps.tex
Makefile update for new diff; minor wording quibble.

To allow rapid composition of libraries using an interface, Spack supports
{\it virtual dependencies}.  A virtual dependency is an abstract name that
represents a library interface (or capability) instead of a library
implementation.  Packages that need this interface do need not to depend on
a specific implementation; they can depend on the virtual name, for which
the user or Spack can select an implementation at build time.
Other package managers support the notion of virtual dependencies, but Spack
adds {\it versioning} to its interfaces, which directly supports concepts 
like MPI versions and BLAS levels.  Spack
handles the details of managing and checking complex versioning constraints.

>>>>

To allow rapid composition of libraries using an interface, Spack supports
{\it virtual dependencies}.  A virtual dependency is an abstract name that
represents a library interface (or capability) instead of a library
implementation.  Packages that need this interface do need not depend on
a specific implementation; they can depend on the virtual name, for which
the user or Spack can select an implementation at build time.
Other package managers support the notion of virtual dependencies, but Spack
adds {\it versioning} to its interfaces, which directly supports concepts 
like MPI versions and BLAS levels.  Spack
handles the details of managing and checking complex versioning constraints.
